Time Series Bootstrapping For Solar Current

### 2021-12-08 deliverables/presentation.Rmd
Simplified presentation slides

- SolarStat: Modeling Photovolatic Sources through Stochastic Markov Processes
    - Marco Miozzo, Davide Zordan, Paolo Dini, and Michele Rossi
- Their objective: Describe how solar irradiance is translated into current output in a PV system throughout the day and cluster results with a Markov model to determine day/night breaks.
- Our objective: Describe how solar irradiance is translated into current output in a PV system and bootsrap results both with and without respect to time, and compare.

@@

- Understanding renewable energy sources like solar power is critical to the next century.
- PV modules installed at individual households/nodes reduce the overall load on the electrical grid.
- Balancing the expected contribution of an individual PV module with the expected residual demand required of the grid is a large optimization problem.
    - We dealt with half of that optimization problem involving the expected contribution of the PV module.

@@

@@

- National Solar Radiation Database (NSRD) from National Renewable Energy Laboratory (NREL) accessed through API
- Los Angeles data (1998-2010) was used to replicate the source paper.
    - Date and time, direct normal irradiance (DNI), and temperature data used.

# Preprocessing

INSERT FIG 1 FROM PAPER HERE
- Astronomical adjustments performed on DNI to find effective solar irradiance:
    - Latitude, longitude, time zone, and the tilt of the earth used in calculations.
    - $I_{eff} \propto I_{sun}cos(\theta)$

# Photovolatic (PV) Module

- Power processing units are attached to PV modules to optimize power output for a given current input.
    - Maximizes power $P=IV$ over a range of possible voltages.
- Result of interest is current output after being adjusted by the power processor and an assumed leakage rate.

>>>>

- _SolarStat: Modeling Photovolatic Sources through Stochastic Markov Processes_

- *Their objective*: 
  - Solar irradiance $\rightarrow$ current output 
  - Cluster results with a Markov model
- *Our objective*: 
  - Solar irradiance $\rightarrow$ current output 
  - Compare iid and time series bootstrap

@@

- Understanding renewable energy sources like solar power is critical to the next century.
- PV modules installed at individual households/nodes reduce the overall load on the electrical grid.
- Balancing the expected contribution of an individual PV module with the expected residual demand required of the grid is a large optimization problem.
    - We dealt with half of that optimization problem

@@

- The paper used data from LA, 1991-2010
- The paper uses ETR (we used similar GHI)
- Simulates for a specific model of small solar panel 
- Panels "laid out" in a 6x6 grid.

@@

- National Solar Radiation Database (NSRDB) from National Renewable Energy
Laboratory (NREL)
- Los Angeles data for 1998-2010

# Overall process

\begin{center}
Raw data (NSRDB)

$\downarrow$

Astronomical adjustment

$\downarrow$

PV module

$\downarrow$

Power processor

$\downarrow$

Bootstrap
\end{center}

# Preprocessing: Astronomical Adjustment

INSERT FIG 1 FROM PAPER HERE
- Astronomical adjustments performed on DNI to find *effective* solar irradiance
- Used: Latitude, longitude, time zone, tilt of the earth 
- $I_{eff} \propto I_{sun}cos(\Theta)$

# Preprocessing: Power processor

- This gives a procedure for translating effective irradiance to
current, given an operating voltage
- Uses:
  - Effective irradiance
  - Operating voltage
  - Properties of solar panel materials
  - Solar panel layout

# Preprocessing: Photovoltaic (PV) Module

- Power processing units are attached to PV modules to optimize power output for a given current input.
- Maximizes power $P=IV$ over voltage
- Here $I$ is a function of $V$
- Result: Optimal current

ADD FIGURES
